Supplementary Information from:\\ \textit{Reconstructing the last known movements of one of Nature's giants}

### 2017-06-28 manuscript/blue-whale-supplementary.tex
Typo

% figure s1
\begin{figure}[!htbp]
  \centering
  \includegraphics[width = \linewidth]{figures/Figure-S1-periodograms.png}
  \caption{Fourier analysis of $delta^{15}$N (A,B) and $delta^{13}$C (C,D) values of the full (A,C) and behavioral phase one only (B,D) components of the baleen plate. Inset values are the two highest frequency spectral densities (in cm). Note the baleen plate is 80cm long. Periodic fluctuation with a distance of 13.5cm along the baleen plate is consistently recovered, but is weaker or absent behavioural phase two} % check legend
  \label{figs1}
\end{figure}

@@

\begin{figure}[!htbp]
  \centering
  \includegraphics[width = \linewidth]{figures/Figure-S3-plankton-d13C-map.png}
  \caption{Isoscape map of the $delta^{13}$C values from POM used as simulated food in the movement model.}
  \label{figs3} 
\end{figure}

>>>>

% figure s1
\begin{figure}[!htbp]
  \centering
  \includegraphics[width = \linewidth]{figures/Figure-S1-periodograms.png}
  \caption{Fourier analysis of $\delta^{15}$N (A,B) and $\delta^{13}$C (C,D) values of the full (A,C) and behavioral phase one only (B,D) components of the baleen plate. Inset values are the two highest frequency spectral densities (in cm). Note the baleen plate is 80cm long. Periodic fluctuation with a distance of 13.5cm along the baleen plate is consistently recovered, but is weaker or absent in behavioural phase two} 
  \label{figs1}
\end{figure}

@@

\begin{figure}[!htbp]
  \centering
  \includegraphics[width = \linewidth]{figures/Figure-S3-plankton-d13C-map.png}
  \caption{Isoscape map of the $\delta^{13}$C values from POM used as simulated food in the movement model.}
  \label{figs3} 
\end{figure}
